---
title: "Load_format_HMD"
author: "Jessica McCordic"
date: "2025-07-17"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## General workflow

For each deployment
- load in HMD data
- summarize to hourly HMD
- summarize to percentiles

```{r Load_libraries}
library(here)
library(PAMscapes)
library(PAMmisc)
library(reshape2)
library(tcltk2) # handles interactively navigating to network file paths
library(tidyverse)
library(tictoc) # allows for time tracking of longer processes
library(svDialogs) # allows for some interactive inputs
#source("AMP_pkgs_funs.R")
```

# Load hybrid millidecade data

The function that handles all the data loading (regardless of format!)
is `checkSoundscapeInput`. You can give this a single file or multiple
files and it will load them up.

```{r Load HMD}


# List all deployment names in given directory

# Since server folders are in a standard structure, use parent folder to get list of all deployments
dep_names <- list.dirs("/home/jmccordic/PassiveAcoustics/DETECTOR_OUTPUT/PYTHON_SOUNDSCAPE_PYPAM/Raw/NEFSC_GOM/", recursive = FALSE)


# ask user which site to run
site_name <- dlg_input(message = "Site name (e.g., 'MONHEGAN')")$res

# select the deployment(s) to load in
dep_list <- as.list(dep_names[which(grepl(site_name, dep_names))])


# Navigate to directory & list netCDF files with HMD data

# set path for directory with netCDF files
# Could maybe set this up as a list for AMP deployments
# could have c("dep1","dep2","dep3") and then use map function 
# for setting directory & running checkSoundscapeInput

# deployment_id <- "PARKSAUSTRALIA_TWOROCKS_202105_TRW"

nc_folder_list <- dep_list |>
  map(~paste0({.}, "/NC")) |>
  unlist()


tic()
hmd_all <- loadMultiscapeData(nc_folder_list, 
                              timeBin = "1hour",
                              binFunction = "median",
                              binCount = TRUE,
                              )
toc()

# loading in 8 deployments took ~37 MINUTES on R container...
# -- might be faster to load individually and stitch together in a separate step?

# hmd_hr <- hmd_all |>
#   # remove HMD values < 10 Hz for better viz
#     select(-c(HMD_0:HMD_9))

# 
#   ncFolder <- paste0(dep_name, "/NC")
#   ncFiles <- list.files(ncFolder, pattern='nc$', full.names=TRUE)
#   
#   tic()
#   hmd_data_hr <- loadSoundscapeData(ncFiles) |>
#     # remove HMD values < 10 Hz for better viz
#     select(-c(HMD_0:HMD_9))|> 
#     # summarize into 1 hour bins
#     binSoundscapeData(bin = "1hour", 
#                       method = "median",
#                       binCount = TRUE) |>
#     # add deployment ID to data
#     mutate(Dep_ID = deployment_id)
#   toc()
  
  write_csv(hmd_all, 
            file = paste0("/home/jmccordic/Jessica.Mccordic/Github/AMP_NPZ_Soundscapes/data/NEFSC_GOM_",site_name, "_HMD_hourlymed.csv"))

# was ~27 seconds in NEFSC office
# ~35 seconds on RStudio container via VPN

  
```

```{r Shiny_explorer}
# explore data in shiny app, also helps figure out which viz function you're interested in
runSoundscapeExplorer(USTR11_HMD)

```

# Annie's working code starting below

```{r}

LUBEC_HMD <- read.csv(here("data/NEFSC_GOM_LUBEC_HMD_hourlymed.csv"))
LUBEC_HMD$site = "Lubec"
LUBEC_HMD$UTC <- as.POSIXct(LUBEC_HMD$UTC, format= "%Y-%m-%dT%H:%M:%SZ", tz = "GMT")
MDR_HMD <- read.csv(here("data/NEFSC_GOM_MDR_HMD_hourlymed.csv"))
MDR_HMD$site = "MDR"
MDR_HMD$UTC <- as.POSIXct(MDR_HMD$UTC, format= "%Y-%m-%dT%H:%M:%SZ", tz = "GMT")
USTR01_HMD <- read.csv(here("data/NEFSC_GOM_USTR01_HMD_hourlymed.csv"))
USTR01_HMD$site = "USTR01"
USTR01_HMD$UTC <- as.POSIXct(USTR01_HMD$UTC, format= "%Y-%m-%dT%H:%M:%SZ", tz = "GMT")
USTR03_HMD <- read.csv(here("data/NEFSC_GOM_USTR03_HMD_hourlymed.csv"))
USTR03_HMD$site = "USTR03"
USTR03_HMD$UTC <- as.POSIXct(USTR03_HMD$UTC, format= "%Y-%m-%dT%H:%M:%SZ", tz = "GMT")
USTR11_HMD <- read.csv(here("data/NEFSC_GOM_USTR11_HMD_hourlymed.csv"))
USTR11_HMD$site = "USTR11"
USTR11_HMD$UTC <- as.POSIXct(USTR11_HMD$UTC, format= "%Y-%m-%dT%H:%M:%SZ", tz = "GMT")
MONHEGAN_HMD <- read.csv(here("data/NEFSC_GOM_MONHEGAN_HMD_hourlymed.csv"))
MONHEGAN_HMD$site = "Monhegan"
MONHEGAN_HMD$UTC <- as.POSIXct(MONHEGAN_HMD$UTC, format= "%Y-%m-%dT%H:%M:%SZ", tz = "GMT")
PORTLAND_HMD <- read.csv(here("data/NEFSC_GOM_PORTLAND_HMD_hourlymed.csv"))
PORTLAND_HMD$site = "Portland"
PORTLAND_HMD$UTC <- as.POSIXct(PORTLAND_HMD$UTC, format= "%Y-%m-%dT%H:%M:%SZ", tz = "GMT")
SB03_HMD <- read.csv(here("data/NEFSC_GOM_SB03_HMD_hourlymed.csv"))
SB03_HMD$site = "SB03"
SB03_HMD$label = "NC"
SB03_HMD$binCount = "60"
SB03_HMD$binCount = as.integer(SB03_HMD$binCount)
SB03_HMD$UTC <- as.POSIXct(SB03_HMD$UTC, format= "%Y-%m-%dT%H:%M:%SZ", tz = "GMT")
SB03_HMD <- SB03_HMD[-c(2,3,4,5,6,7,8,9,10,11)]
#SB03_HMD <- SB03_HMD[-c(20)]
YORK_HMD <- read.csv(here("data/NEFSC_GOM_YORK_HMD_hourlymed.csv"))
YORK_HMD$site = "York"
YORK_HMD$label = "NC"
YORK_HMD$binCount = "60"
YORK_HMD$binCount = as.integer(YORK_HMD$binCount)
YORK_HMD$UTC <- as.POSIXct(YORK_HMD$UTC, format= "%Y-%m-%dT%H:%M:%SZ", tz = "GMT")


```

#plots

```{r}
USTR_sites <- USTR01_HMD %>%
  full_join(USTR03_HMD)%>%
  full_join(USTR11_HMD)

coastal_sites <- LUBEC_HMD %>% #coastal sites and SB03
  full_join(MDR_HMD) %>%
  full_join(MONHEGAN_HMD) %>%
  full_join(PORTLAND_HMD) %>%
  full_join(YORK_HMD)%>%
  full_join(SB03_HMD)
  
ALL_sites <- USTR_sites %>%
  full_join(coastal_sites)

runSoundscapeExplorer(USTR_sites)

plotPSD(x=SB03_HMD, style='quantile', q=0.99)+
  labs(y= (expression(paste("Power Spectral Density dB re 1 \u00b5Pa" ^ "2", "/Hz"))))+
  theme_bw()

all_sites <- plotPSD(x=ALL_sites, style='quantile', q=0.99, facet='site')+
  labs(y= (expression(paste("Power Spectral Density dB re 1 \u00b5Pa" ^ "2", "/Hz"))))+
  theme_bw()+
  guides(color= guide_legend(title= "Site"))

all_sites_month<- plotPSD(x=ALL_sites, style='quantile', q=0, by='month', facet= 'site') +
  labs(y= (expression(paste("Power Spectral Density dB re 1 \u00b5Pa" ^ "2", "/Hz"))))+
  theme_bw()+
  guides(color= guide_legend(title= "Month"))



ggsave(here("figs", "all_sites_month.png"), all_sites_month, width= 14, height= 10, units= "in")
ggsave(here("figs", "all_sites.png"), all_sites, width= 14, height= 10, units= "in")

```
# LTSAs

```{r}

USTR01_LTSA = plotLTSA(x= USTR01_HMD,
                       title = "USTR01")
USTR03_LTSA = plotLTSA(x= USTR03_HMD,
                       title = "USTR03")
USTR11_LTSA = plotLTSA(x= USTR11_HMD,
                       title = "USTR11")
LUBEC_LTSA = plotLTSA(x= LUBEC_HMD,
                       title = "Lubec")
MDR_LTSA = plotLTSA(x= MDR_HMD,
                       title = "MDR")
MONHEGAN_LTSA = plotLTSA(x= MONHEGAN_HMD,
                       title = "Monhegan")
PORTLAND_LTSA = plotLTSA(x= PORTLAND_HMD,
                       title = "Portland")
YORK_LTSA = plotLTSA(x= YORK_HMD,
                       title = "York")
SB03_LTSA = plotLTSA(x= SB03_HMD,
                       title = "SB03")


allSites_LTSA = plotLTSA(x=ALL_sites, facet= 'site')+
  theme_bw()
ggsave(here("figs", "allSites_LTSAs.png"), allSites_LTSA, width= 14, height= 12, units= "in")


plot(allSites_LTSA)


```
#seasonal octave level plots
```{r}
#convert to OLs

LUBEC_OL <- createOctaveLevel(LUBEC_HMD, type= 'ol')
MDR_OL <- createOctaveLevel(MDR_HMD, type= 'ol')
MONHEGAN_OL <- createOctaveLevel(MONHEGAN_HMD, type= 'ol')
PORTLAND_OL <- createOctaveLevel(PORTLAND_HMD, type= 'ol')
SB03_OL <- createOctaveLevel(SB03_HMD, type= 'ol')
USTR01_OL <- createOctaveLevel(USTR01_HMD, type= 'ol')
USTR03_OL <- createOctaveLevel(USTR03_HMD, type= 'ol')
USTR11_OL <- createOctaveLevel(USTR11_HMD, type= 'ol')
YORK_OL <- createOctaveLevel(YORK_HMD, type= 'ol')

all_OLSites <- LUBEC_OL %>%
  full_join(MDR_OL) %>%
  full_join(MONHEGAN_OL) %>%
  full_join(PORTLAND_OL) %>%
  full_join(YORK_OL) %>%
  full_join(SB03_OL) %>%
  full_join(USTR01_OL) %>%
  full_join(USTR03_OL) %>%
  full_join(USTR11_OL)

all_OLSites$month <- month(all_OLSites$UTC)

all_OLSites$season = case_when(all_OLSites$month == 1 ~ "winter",
                            all_OLSites$month == 2 ~ "winter",
                            all_OLSites$month == 3 ~ "spring",
                            all_OLSites$month == 4 ~ "spring",
                            all_OLSites$month == 5 ~ "spring",
                            all_OLSites$month == 6 ~ "summer",
                            all_OLSites$month == 7 ~ "summer",
                            all_OLSites$month == 8 ~ "summer",
                            all_OLSites$month == 9 ~ "fall",
                            all_OLSites$month == 10 ~ "fall",
                            all_OLSites$month == 11 ~ "fall",
                            all_OLSites$month == 12 ~ "winter")
  
all_OLSiteSeason<- all_OLSites %>% 
  group_by(season, site) %>% 
  dplyr::summarize(med_16 = median(OL_16, na.rm=TRUE),med_31.5 = median(OL_31.5, na.rm=TRUE),med_63 = median(OL_63, na.rm=TRUE),med_125 = median(OL_125, na.rm=TRUE),med_250 = median(OL_250, na.rm=TRUE),med_500 = median(OL_500, na.rm=TRUE), med_1000 = median(OL_1000, na.rm=TRUE),med_2000= median(OL_2000, na.rm= TRUE), med_4000 = median(OL_4000, na.rm=TRUE),med_8000= median(OL_8000, na.rm= TRUE), med_16000 = median(OL_16000, na.rm=TRUE))


melted_all_OLSiteSeason <- melt(all_OLSiteSeason, id= c("season", "site"), variable.name= "TOL_band",
                                value.name= "med_seasonal_SPL")

melted_all_OLSiteSeason$season = factor(melted_all_OLSiteSeason$season,
                                        levels= c("winter", "spring", "summer", "fall"),
                                        labels= c("Winter", "Spring", "Summer", "Fall"))
melted_all_OLSiteSeason$OL_band = factor(melted_all_OLSiteSeason$OL_band,
                                        levels= c("med_16", "med_31.5", "med_63", "med_125", "med_250", "med_500", "med_1000", "med_2000", "med_4000", "med_8000", "med_16000"),
                                        labels= c("16", "31.5", "63", "125", "250","500", "1000", "2000", "4000", "8000", "16000"))

ggplot(melted_all_OLSiteSeason, aes(x= OL_band, y = med_seasonal_SPL, color= season, group= season))+
  geom_point()+ geom_line() +
  facet_wrap(factor(site, levels = c('Lubec', 'MDR', 'Monhegan', 'Portland', 'SB03', 'USTR01', 'USTR03', 'USTR11', 'York'))~., ncol= 3)+
  theme_bw()+
  xlab("Octave band (Hz)")+
  ylab(expression(paste('Median sound pressure levels (db re 1 \u00b5Pa)')))+
  scale_color_manual(values= c("#5761C0", "#4B8320", "#DB2207","#FFAB38"))+
  guides(color= guide_legend(title= "Season"))

```
#TOBs
```{r}

#convert to TOLs

LUBEC_TOL <- createOctaveLevel(LUBEC_HMD, type= 'tol')
MDR_TOL <- createOctaveLevel(MDR_HMD, type= 'tol')
MONHEGAN_TOL <- createOctaveLevel(MONHEGAN_HMD, type= 'tol')
PORTLAND_TOL <- createOctaveLevel(PORTLAND_HMD, type= 'tol')
SB03_TOL <- createOctaveLevel(SB03_HMD, type= 'tol')
USTR01_TOL <- createOctaveLevel(USTR01_HMD, type= 'tol')
USTR03_TOL <- createOctaveLevel(USTR03_HMD, type= 'tol')
USTR11_TOL <- createOctaveLevel(USTR11_HMD, type= 'tol')
YORK_TOL <- createOctaveLevel(YORK_HMD, type= 'tol')

all_TOLSites <- LUBEC_TOL %>%
  full_join(MDR_TOL) %>%
  full_join(MONHEGAN_TOL) %>%
  full_join(PORTLAND_TOL) %>%
  full_join(YORK_TOL) %>%
  full_join(SB03_TOL) %>%
  full_join(USTR01_TOL) %>%
  full_join(USTR03_TOL) %>%
  full_join(USTR11_TOL)

all_TOLSites$month <- month(all_TOLSites$UTC)

all_TOLSites$season = case_when(all_TOLSites$month == 1 ~ "winter",
                            all_TOLSites$month == 2 ~ "winter",
                            all_TOLSites$month == 3 ~ "spring",
                            all_TOLSites$month == 4 ~ "spring",
                            all_TOLSites$month == 5 ~ "spring",
                            all_TOLSites$month == 6 ~ "summer",
                            all_TOLSites$month == 7 ~ "summer",
                            all_TOLSites$month == 8 ~ "summer",
                            all_TOLSites$month == 9 ~ "fall",
                            all_TOLSites$month == 10 ~ "fall",
                            all_TOLSites$month == 11 ~ "fall",
                            all_TOLSites$month == 12 ~ "winter")
  
all_TOLSiteSeason<- all_TOLSites %>% 
  group_by(season, site) %>% 
  dplyr::summarize(med_16 = median(TOL_16, na.rm=TRUE), med_20= median(TOL_20, med_25 = median(TOL_25, na.rm=TRUE), na.rm=TRUE), med_31.5 = median(TOL_31.5, na.rm=TRUE), med_40 = median(TOL_40, na.rm=TRUE), med_50 = median(TOL_50, na.rm=TRUE), med_63 = median(TOL_63, na.rm=TRUE),med_80 = median(TOL_80, na.rm=TRUE), med_100 = median(TOL_100, na.rm=TRUE), med_125 = median(TOL_125, na.rm=TRUE),med_160 = median(TOL_160, na.rm=TRUE), med_200 = median(TOL_200, na.rm=TRUE), med_250 = median(TOL_250, na.rm=TRUE), med_315 = median(TOL_315, na.rm=TRUE), med_400 = median(TOL_400, na.rm=TRUE),med_500 = median(TOL_500, na.rm=TRUE), med_630 = median(TOL_630, na.rm=TRUE), med_800 = median(TOL_800, na.rm=TRUE),med_1000 = median(TOL_1000, na.rm=TRUE), med_1250 = median(TOL_1250, na.rm=TRUE), med_1600 = median(TOL_1600, na.rm=TRUE),med_2000= median(TOL_2000, na.rm= TRUE),med_2500 = median(TOL_2500, na.rm=TRUE), med_3150 = median(TOL_3150, na.rm=TRUE),med_4000 = median(TOL_4000, na.rm=TRUE), med_5000 = median(TOL_5000, na.rm=TRUE), med_6300 = median(TOL_6300, na.rm=TRUE),med_8000= median(TOL_8000, na.rm= TRUE),med_10000 = median(TOL_10000, na.rm=TRUE), med_12500 = median(TOL_12500, na.rm=TRUE),med_16000 = median(TOL_16000, na.rm=TRUE), med_20000 = median(TOL_20000, na.rm=TRUE))


melted_all_TOLSiteSeason <- melt(all_TOLSiteSeason, id= c("season", "site"), variable.name= "TOL_band",
                                value.name= "med_seasonal_SPL")

melted_all_TOLSiteSeason$season = factor(melted_all_TOLSiteSeason$season,
                                        levels= c("winter", "spring", "summer", "fall"),
                                        labels= c("Winter", "Spring", "Summer", "Fall"))
melted_all_TOLSiteSeason$TOL_band = factor(melted_all_TOLSiteSeason$TOL_band,
                                        levels= c("med_16","med_20","med_25","med_31.5","med_40","med_50", "med_63","med_80","med_100", "med_125","med_160","med_200", "med_250","med_315","med_400", "med_500","med_630","med_800", "med_1000","med_1250","med_1600", "med_2000","med_2500","med_3150", "med_4000","med_5000","med_6300", "med_8000","med_10000","med_12500", "med_16000", "med_20000"),
                                        labels= c("16", "20", "25", "31.5", "40", "50", "63", "80", "100", "125", "160", "200", "250", "315", "400", "500", "630", "800", "1000", "1250", "1600", "2000", "2500", "3150", "4000", "5000", "6300", "8000", "10000", "12500", "16000", "20000"))

ggplot(melted_all_TOLSiteSeason, aes(x= TOL_band, y = med_seasonal_SPL, color= season, group= season))+
  geom_point(size= 1)+ geom_line() +
  facet_wrap(factor(site, levels = c('Lubec', 'MDR', 'Monhegan', 'Portland', 'SB03', 'USTR01', 'USTR03', 'USTR11', 'York'))~., ncol= 3)+
  theme_bw()+
  xlab("Third-octave band (Hz)")+
  ylab(expression(paste('Median sound pressure levels (db re 1 \u00b5Pa)')))+
  scale_color_manual(values= c("#5761C0", "#4B8320", "#DB2207","#FFAB38"))+
  guides(color= guide_legend(title= "Season"))+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))




```